---
title: "Investigating plottting interactions logistic regression"
author: "Eamonn O'Brien<br><small><br>Biostatistics<br></small>"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    thumbnails: false
    lightbox: false
    gallery: false
    highlight: tango
    use_bookdown: true
    toc_depth: 3
    fig_caption: true
    code_folding: hide
link-citations: yes
description: "xxxxxx"
---
<style>
.table {
	width: 50%;
}
p.caption {
  font-size: 0.8em;
  color: DarkBlue;
}
body { 
	max-width: 1900px; 
	margin: 0 auto !important; 
	margin-right: 0 !important;
	float: none !important; 
}
</style>

```{css, echo=FALSE}

 
```


```{r setup,echo=FALSE,include=FALSE}

    set.seed(1234)
    library(rms)          # automatically engages rms(Hmisc)
    library(tidyverse)
    library(kableExtra) 
    library(knitr) 
    library(reshape)
    library(rms)
    library(ggplot2)
    require(gridExtra)

    knitrSet(lang='markdown', w=7, h=7, dev='svg', fig.path='folder/')
    options(prType='html')
    options(width=200)
    
    # format function 
       formatz <- function(x){
          if (!is.na(x)  ) {
            sprintf(x, fmt = '%#.1f')  
           }
       }
     
    options(max.print=1000000)    
    options(scipen=999)
    
    ## convenience functions
    p0 <- function(x) {formatC(x, format="f", digits=1)}
    p1 <- function(x) {formatC(x, format="f", digits=1)}
    p2 <- function(x) {formatC(x, format="f", digits=2)}
    p3 <- function(x) {formatC(x, format="f", digits=3)}
    p4 <- function(x) {formatC(x, format="f", digits=4)}
    p5 <- function(x) {formatC(x, format="f", digits=5)}
    
    logit <-     function(p) log(1/(1/p-1))
    expit <-     function(x) 1/(1/exp(x) + 1)
    inv_logit <- function(logit) exp(logit) / (1 + exp(logit))
    is.even <-   function(x){ x %% 2 == 0 }                       # function to id. odd maybe useful
    options(width=200)


```

# Introduction

Simulate logistic regression and focus on one factor's interaction with treatment and how we should present the redults

```{r, }

    # select the design to simulate
    Design = "Treatment interacts with all variables" 
    #Design = "Treatment interacts with smoking only" 
    #Design = "No-interaction logit-additive model"
    
    # coefficients on log odds scale
    
    intercept <- -3
    n=1000
    v1 = 1
    v2 = 1/(65-18)
    v3 = 0.4
    v4 = 0
    v5 = 1/3
    v6 = -.5/10
    v7 = 0.25/30
    v8 = -.1/10
    v9 = -1/50
    v10 = log(2)
    v11 = -log(1)
    v12 = log(0.5)
    
    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    randomi <- runif(n)    # this determines Y=1 later, 
    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    
    trt.coef       <-  v1     # log odds ratio so 1 -> 2.718, so 1 is LARGE
    age.coef       <-  v2     # log odds of 1 over the age range
    smoke.coef     <-  v3     # this is odds of 1.5
    bmi.coef       <-  v4     # this is an odds of 1..50:50
    covar3.coef    <-  v5     # log odds 1 over range of 3
    covar1.coef    <-  v6     # log odds -.05 per unit change
    vas.coef       <-  v7     # log odds .008 per unit change. log odds .25 over 30 units odds 1.27
    time.coef      <-  v8     # log odds -.01 per year, log odds -.1 over 10 years or odds .90
    covar2.coef    <-  v9     # log odds 0.02 per unit, log odds 1 over 50 units or odds 2.7
    fact1.coef     <-  v10    # log odds 0.693 per change in binary, or odds of 2   
    binary2.coef   <-  v11    # log odds 0 per change in binary, or odds of 1  
    sex.coef       <-  v12    # log odds -0.693 per change in binary, or odds of .5  
    
    # made up data structure 
    trt      <- sample(1:3,   n, replace=TRUE)      # trt 3 levels
    age      <- sample(18:65, n, replace=TRUE)      # continuous
    bmi      <- sample(1:3,   n, replace=TRUE)      # assume 3 equal groups
    smoking  <- sample(1:3,   n, replace=TRUE)      # categorical assume 3 equal groups
    covar3   <- round(runif(n,0,3),2)
    covar1   <- round(runif(n,0,10),2)
    vas      <- sample(1:30, n, replace=TRUE)
    time     <- round(runif(n,0,10),2)              # years
    covar2   <- sample(1:50, n, replace=TRUE)
    fact1    <- sample(0:1,  n, replace=TRUE)
    binary2  <- sample(0:1,  n, replace=TRUE)
    sex      <- sample(0:1,  n, replace=TRUE)


```

# Linear predictor

Create linear predictors

```{r, }

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~linear predictor
if ( ( Design) == "Treatment interacts with all variables" )  {
  
  lp = intercept + trt*trt.coef*(smoking*smoke.coef   +   age*age.coef  + bmi*bmi.coef   + covar3*covar3.coef +
                                   covar1*covar1.coef +   vas*vas.coef  + time*time.coef + covar2*covar2.coef +
                                   fact1*fact1.coef   +
                                   binary2*binary2.coef + sex*sex.coef) 
  
  
}   else if ( ( Design ) == "Treatment interacts with smoking only" ) {    
  
  # truth  only smoking interacts  with trt
  lp = intercept + (trt*trt.coef*smoking*smoke.coef)   +   age*age.coef   + bmi*bmi.coef + covar3*covar3.coef +
    covar1*covar1.coef  + vas*vas.coef   + time*time.coef + covar2*covar2.coef + fact1*fact1.coef +
    binary2*binary2.coef + sex*sex.coef
  
  
}   else if ( ( Design) == "No-interaction logit-additive model" ) {  
  
  # truth no interactions
  lp = intercept + trt*trt.coef + smoking*smoke.coef + age*age.coef  + bmi*bmi.coef  + covar3*covar3.coef  +
    covar1*covar1.coef + vas*vas.coef  + time*time.coef + covar2*covar2.coef + fact1*fact1.coef +
    binary2*binary2.coef + sex*sex.coef
}

y <- ifelse(randomi < plogis(lp), 1, 0)   # one liner  randomi object is necessary for R shiny only



```

# Dataset creation

Stick the linear predictor and covariates together

```{r, }


    datx <- data.frame(cbind(y,  trt ,smoking,  age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi))
    
    da <-  datx 
    
    da$trt <-     factor(da$trt)
    da$smoking <- factor(da$smoking)
    da$fact1 <-   factor(da$fact1)
    da$binary2 <- factor(da$binary2)
    da$sex <-     factor(da$sex)
    da$bmi <-     factor(da$bmi)
    
    # labels for forest plots
    label(da$age)                <- 'Age'                       
    label(da$trt)                <- 'Treatment'
    label(da$bmi)                <- 'Body Mass Index'
    label(da$smoking)            <- 'Smoking'
    label(da$covar3)             <- 'Biomarker'
    label(da$covar1)             <- 'Blood score'
    label(da$vas)                <- 'Visual analogue score'
    label(da$time)               <- 'Time since diagnosis'
    label(da$covar2)             <- 'Fitness score'
    label(da$fact1)              <- "History"
    label(da$binary2)            <- "Employed"
    label(da$sex)                <- 'Sex'
    
    dd <<- datadist(da)
    options(datadist="dd")


```

# Regression

Run logistic regression

```{r, results='asis'}

# RUN REGRESSONS
    A<-lrm(y~   trt * (smoking  + age  + bmi + covar3 + covar1 + vas + time + covar2 + fact1 + binary2 +sex),da, y=TRUE ,x=TRUE)  # all interact with trt
    B<-lrm(y~  (trt *  smoking) + age  + bmi + covar3 + covar1 + vas + time + covar2 + fact1 + binary2 +sex, da, y=TRUE, x=TRUE)  # smoking * trt only
    C<-lrm(y~   trt +  smoking  + age +  bmi + covar3 + covar1 + vas + time + covar2 + fact1 + binary2 +sex, da, y=TRUE, x=TRUE)  # main effect
  
```

# Likelihood regression test 

Treatment interacting with all covariates vrs No-interaction logit-additive model

```{r, results='asis'}   
  #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  # LRTESTS
  #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
   
  
  lrtest( A, C)
   
```

# Three Summaries if regression models  

Treatment interacting with all covariates vrs No-interaction logit-additive model

```{r, results='asis'}   
   
  (A1 <- summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=1, est.all=FALSE, vnames=c( "labels")))
  
  (A2 <- summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=2, est.all=FALSE, vnames=c( "labels")))
  
  (A3 <- summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=3, est.all=FALSE, vnames=c( "labels")))

 
```

# Plot summaries

A bit cramped but a useful plot.

```{r, }

  par(mfrow=c(1,3)) 
  
  par(oma=c(3,6,1,1)) 
  
  options(digits=1)
  
  plot(summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=1, est.all=FALSE, vnames=c( "labels")), 
       log=TRUE, xlim=c(log(.01),log(40)),
       q=c(  0.95 ), at=c(.02,0.05,.1,.2,.5,1,2,4,8,20), lwd=3, pch=17,
       col=   rgb(red=.4,green=.1,blue=.5,alpha=c(.5,.3,.2)),
       col.points='black', cex=1, main= "Odds Ratio (Treatment 1)", cex.main=1.8
  )
  
  plot(summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=2, est.all=FALSE, vnames=c( "labels")), 
       log=TRUE, xlim=c(log(.01),log(40)),
       q=c(  0.95 ), at=c(.02,0.05,.1,.2,.5,1,2,4,8,20), lwd=3, pch=17,
       col=   rgb(red=.4,green=.1,blue=.5,alpha=c(.5,.3,.2)),
       col.points='black', cex=1, main= "Odds Ratio (Treatment 2)", cex.main=1.8
  )
  
  plot(summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=3, est.all=FALSE, vnames=c( "labels")), 
       log=TRUE, xlim=c(log(.01),log(40)),
       q=c(  0.95 ), at=c(.02,0.05,.1,.2,.5,1,2,4,8,20), lwd=3, pch=17,
       col=   rgb(red=.4,green=.1,blue=.5,alpha=c(.5,.3,.2)),
       col.points='black', cex=1, main= "Odds Ratio (Treatment 3)", cex.main=1.8
  )
  
  par(mfrow=c(1,1))


```

# Presentation of fact1 and treatment interaction

Contrasts comparing fact1 within each treatment

```{r, } 

  options(digits=6)
  k1 <- contrast(A, list(fact1=c(0,1), trt=c(2)), list(fact1=c(0,1), trt=c(1)) , fun=exp) 
  z1 <- print(k1, X=TRUE)   
  
  k2 <- contrast(A, list(fact1=c(0,1), trt=c(3)), list(fact1=c(0,1), trt=c(1)) , fun=exp) 
  z2 <- print(k2, X=TRUE)   
  
  k3 <- contrast(A, list(fact1=c(0,1), trt=c(3)), list(fact1=c(0,1), trt=c(2)) , fun=exp) 
  z3 <- print(k3, X=TRUE)   


```

# Presentation of fact1 and treatment interaction, plotting

Function to plot the results

```{r, } 
 
int.plot <- function(k1, factor.="factor of interest",
                     effect="Treatment 2 - Treatment 1", 
                     first.grp="Absent", 
                     second.grp="Present") {
  
  zz <- k1
  # log scale
  Scorex=as.vector(zz$Contrast)
  lbx =  as.vector(zz$Lower)
  ubx =  as.vector(zz$Upper)
  
  df.plot <- data.frame(x=c(effect,effect),
                        factor.=c(first.grp,second.grp ),
                        Score=exp(Scorex),
                        lb = exp(lbx),
                        ub =exp(ubx))
  
  df.plot$factor. = factor(df.plot$factor., 
                           levels = c(first.grp,second.grp ))
   
  
  gp <- ggplot(df.plot, aes(x=factor., y=log(Score), fill="black", group=x))
  gg <- gp + #geom_line(aes(linetype=x), size=.6) + 
    geom_point(aes(shape=x), size=3) + 
    geom_errorbar(aes(ymax=log(ub), ymin=log(lb)), width=.1) +
    theme(legend.position="none") + ylab("Odds Ratio (OR > 1 better outcomes) ") + xlab(factor.) +
    
    geom_hline(yintercept=log(1), linetype="dashed", color = "blue") +
    
    scale_y_continuous(
      breaks= log(c(1/32,1/16,1/8, 1/4,1/2,  1, 2, 4 ,8, 16,32,64, 128) )  ,  
      limits = c(log(1/12),log(128)),  
      labels=     c(1/32,1/16,1/8, 1/4,1/2,  1, 2, 4 ,8, 16,32,64,128)
    ) +
    
    coord_flip() +
    
    geom_text(aes(   
      y=log(40),
      label = paste0(p3(Score),", 95%CI (" ,p3(lb),", ",p3(ub), ")"), 
      vjust=-1.0), size=2.8, color='blue') +
    
    ggtitle( paste0("Odds ratio of ASAS20 response for ", effect) )
  
  
    gg <- gg + labs(caption = c("Interaction p-value 0.0xx, test the necessity of the orange interaction", 
                              "Interaction present if the pattern differs between factors")) + 
    theme(plot.caption = element_text(hjust=c(1, 0)))
  
  # Add text and arrows
  i <- gg + geom_segment(
    x = 1.5, y =  Scorex[1],
    xend = 1.5, yend =  Scorex[2],
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = .5, 
    arrow = arrow(length = unit(0.2, "cm")),
    colour = "#EC7014" # Also accepts "red", "blue' etc
  ) 
  
  k <- i + geom_text( aes(
    x = 1.5, y = (Scorex[1]+Scorex[2])/2,
    label = paste0("Odds of response ",p0(exp(   max(Scorex[2],Scorex[1]) -  min(Scorex[2],Scorex[1])  ))," x"), 
    group = NULL,
    vjust = -1, #.3
    hjust = .7 #1
  ), size=2.8 , color="#EC7014") 
   
}


```

#  Execute contrasts within Factor and plot function

Treatment comparison for each factor levels

```{r, } 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  age.=sample(30:80,1)  # showing it is the interaction that counts.
  
  options(digits=6)
  k1 <- contrast(A, list(fact1=c(0,1),age=age., trt=c(2)), list(fact1=c(0,1), age=age.,trt=c(1)) , fun=exp) 
  z1 <- print(k1, X=TRUE)   
  
  k2 <- contrast(A, list(fact1=c(0,1), age=age.,trt=c(3)), list(fact1=c(0,1), age=age.,trt=c(1)) , fun=exp) 
  z2 <- print(k2, X=TRUE)   
  
  k3 <- contrast(A, list(fact1=c(0,1), age=age.,trt=c(3)), list(fact1=c(0,1), age=age.,trt=c(2)) , fun=exp) 
  z3 <- print(k3, X=TRUE)   
 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# execute function
  p1x <- int.plot(k1, factor.="factor of interest",
                  effect="Treatment 2 - Treatment 1", 
                  first.grp="Absent", 
                  second.grp="Present") 
  
  
  p2x <- int.plot(k2, factor.="factor of interest",
                  effect="Treatment 3 - Treatment 1", 
                  first.grp="Absent", 
                  second.grp="Present") 
  
  
  p3x <-int.plot(k3, factor.="factor of interest",
                 effect="Treatment 3 - Treatment 2", 
                 first.grp="Absent", 
               second.grp="Present") 

```

#  Execute plot function

Treatment comparison for each factor levels

```{r,}

# its only the orange that is important. And will not change if other values in model are altered.
# the actual OR will change if the covariates change, but the same amount in both levels.
# should mention the values that are held constant!
grid.arrange(p1x,p2x,p3x)
# A
# lrtest(A,C)
# anova(A)
 

```

#  Now contrasts within treatment

This is the way we presented, is the previous way better?

```{r, results='hide'} 

  # now try the original approach
  age.=sample(30:80,1)  # showing it is the interaction that counts.
  
  options(digits=6)
  k1 <- contrast(A, list(fact1=c(1),age=age., trt=c(1)), list(fact1=c(0), age=age.,trt=c(1)) , fun=exp) 
  z1 <- print(k1, X=TRUE)   
  
  k2 <- contrast(A, list(fact1=c(1), age=age.,trt=c(2)), list(fact1=c(0), age=age.,trt=c(2)) , fun=exp) 
  z2 <- print(k2, X=TRUE)   
  
  k3 <- contrast(A, list(fact1=c(1),  age=age.,trt=c(3)), list(fact1=c(0),  age=age.,trt=c(3)) , fun=exp) 
  z3 <- print(k3, X=TRUE)   

  
```

```{r, } 
  
  zz<-rbind(k1,k2,k3)
  zz<-zz[,c("Contrast","Lower","Upper")]
  zz<- unlist(zz)
  zz<-matrix(zz, nrow=3, ncol=3)
  zz<-as.data.frame(zz)
  names(zz) <-c("Score","lb","ub")
  zz<-data.frame(zz)
  zze <- exp(zz)

  df.plot <- data.frame(x=c("Treatment","Treatment", "Treatment"),
                        factor.=c("Placebo","150mg","300mg"),
                        Score=exp(zz$Score),
                        lb = exp(zz$lb),
                        ub =exp(zz$ub))
   
 # df.plot$factor. = factor(df.plot$factor., levels = c("Placebo","150mg","300mg"))
  df.plot$factor. = factor(df.plot$factor., levels = c("300mg", "150mg", "Placebo"))
 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 
 
  gp <- ggplot(df.plot, aes(x=factor., y=log(Score), fill="black", group=x))
  gg <- gp + #geom_line(aes(linetype=x), size=.6) + 
    geom_point(aes(shape=x), size=3) + 
    geom_errorbar(aes(ymax=log(ub), ymin=log(lb)), width=.1) +
    theme(legend.position="none") + ylab("Odds Ratio") + xlab("Treatment") +
    
    geom_hline(yintercept=log(1), linetype="dashed", color = "blue") +
    
    scale_y_continuous(
      breaks= log(c(1/64,1/32,1/16,1/8, 1/4,1/2,  1, 2, 4 ,8, 16,32,64, 128) )  ,  
      limits = c(log(1/32),log(128)),  
      labels=     c(1/64,1/32,1/16,1/8, 1/4,1/2,  1, 2, 4 ,8, 16,32,64,128)
    ) +
    
    coord_flip() +
   
    geom_text(aes(  y=log(40) ,label = paste0(p3(zze$Score),", 95%CI (" ,p3(zze$lb),", ",p3(zze$ub), ")"), 
                    vjust=-1.0), size=2.8, color='blue') +
     
    ggtitle( "Nail Dystrophy (Present v Absent) Odds ratio of ASAS20 response by treatment") 
  
    gg <- gg + labs(caption = c("Interaction p-value 0.0xx, test the necessity of the two orange interactions", "Interaction present if the pattern differs across treatments\nOdds ratio > 1 better outcomes")) + 
    theme(plot.caption = element_text(hjust=c(1, 0)))
   
    ## add arrows
  i <- gg + geom_segment(
    x = 2.5, y =  zz$Score[1],
    xend = 2.5, yend =  zz$Score[2],
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = .5, 
    arrow = arrow(length = unit(0.2, "cm")),
    colour = "#EC7014" # Also accepts "red", "blue' etc
  ) 
  
  ## add arrows
  j <- i + geom_segment(
    x = 1.5, y =  zz$Score[2],
    xend = 1.5, yend =  zz$Score[3],
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = .5, 
    arrow = arrow(length = unit(0.2, "cm")),
    colour = "#EC7014" # Also accepts "red", "blue' etc
  ) 
  
  ## add text to accompany arrow
  k <- j + geom_text( aes(
    x = 2.5, y = (zz$Score[1]+zz$Score[2])/2,
    label = paste0("150mg v placebo odds of response ",
                   p0(exp(   max(zz$Score[2],zz$Score[1]) -  min(zz$Score[2],zz$Score[1])  ))," x "), 
    group = NULL,
    vjust = -1, #.3
    hjust = .5
  ), size=2.8 , color="#EC7014") 
  
  ## add text to accompany arrow
  m <- k + geom_text( aes(
    x = 1.5, y = ((zz$Score[2]+zz$Score[3])/2),
    label = paste0("300mg v 150mg odds of response ",
                   p0(exp(   max(zz$Score[3],zz$Score[2]) -  min(zz$Score[3],zz$Score[2])  ))," x "), 
    group = NULL,
    vjust = -1,
    hjust = .5
  ), size=2.8 , color="#EC7014") 
  
  # add text
  n <- m + geom_text( aes(
    x = 3, y = log(40),
    label = "OR: Present v Absent", 
    group = NULL,
    vjust = - 3, #.3
    hjust = .5 #1
  ), size=2.8 , color="blue") 
  
  
   q <- n + geom_text( aes(
    x = 0.5, y = ((zz$Score[1]+zz$Score[3])/2),
    label = paste0("300mg v placebo odds of response ",
                   p0(exp(   max(zz$Score[3],zz$Score[1]) -  min(zz$Score[3],zz$Score[1])  ))," x "), 
    group = NULL,
    vjust = -1,
    hjust = .5
  ), size=2.8 , color="#EC7014") 
   
   
     
  ## add arrows
  r <- q + geom_segment(
    x = 0.5, y =  zz$Score[1],
    xend = 0.5, yend =  zz$Score[3],
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = .5, 
    arrow = arrow(length = unit(0.2, "cm")),
    colour = "#EC7014" # Also accepts "red", "blue' etc
  ) 
  
  
  
```

#  Execute plot

Treatment comparison within treatments

```{r,}  
  
  r


```

#  The interaction model


```{r, results='asis'}  
  
  A


```

#  The interaction model anova


```{r, results='asis'}  
  
     x <- anova(A, india=FALSE, vnames='labels' )
    print(x, which=c( 'subscripts' ))
    
```

#  conclusion

We have evidence against the assumption that the overall effect of treatment is applicable to all patients.

Interactions are the key. 

In section 11, we see plots that might be more intuitive, the treatment effect within a covariate's levels.

As the factor of interest only interacts with treatment. The values of the other covarites do not change the magnitude of the interaction (eg changing age, just shift both effects by the same amount).

So in figure 13 comparing 150mg v placebo the interaction effect quoted in orange applies equally also to the treatment effect comparing factor levels.

That is the interaction comparing 150mg v placebo is the same effect comparing absent v present...and so on.

We can examine the regression table and see these effects directly (one comparison will not be presented as comparisons are made to a reference). 

So the answer can be found by examining 'trt=2 × fact1=1' and 'trt=3 × fact1=1' and of course exponentiating the coefficients. 

Examine the anova table and look at the interaction hypothesis test p-value to see if the interaction test for the factor provides evidence against the null of no interaction.



```{r,}  



```

# References

https://www.fharrell.com/post/path/
https://www.fharrell.com/post/covadj/
https://www.fharrell.com/post/ia/
https://www.fharrell.com/post/varyor/




```{r,}  



```

# Computing Environment

`r markupSpecs$html$session()`