---
title: "AE reporting"
author: "Eamonn O'Brien<br><small><br>Biostatistics<br></small>"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    thumbnails: false
    lightbox: false
    gallery: false
    highlight: tango
    use_bookdown: true
    toc_depth: 3
    fig_caption: true
    code_folding: hide
link-citations: yes
description: "xxxxxx"
---
<style>
.table {
	width: 50%;
}
p.caption {
  font-size: 0.8em;
  color: DarkBlue;
}
body { 
	max-width: 1900px; 
	margin: 0 auto !important; 
	margin-right: 0 !important;
	float: none !important; 
}
</style>

```{css, echo=FALSE}

 
```


```{r setup,echo=FALSE,include=FALSE}

  set.seed(124)
  library(rms)          # automatically engages rms(Hmisc)
  library(tidyverse)
  library(kableExtra) 
  library(knitr) 
  library(reshape)
  library(rms)
  
  
  knitrSet(lang='markdown', w=7, h=7, dev='svg', fig.path='folder/')
  options(prType='html')
  options(width=200)
  
  # format function 
     formatz <- function(x){
        if (!is.na(x)  ) {
          sprintf(x, fmt = '%#.1f')  
         }
     }
     
     

    options(max.print=1000000)    
    options(scipen=999)
    
    ## convenience functions
    p0 <- function(x) {formatC(x, format="f", digits=1)}
    p1 <- function(x) {formatC(x, format="f", digits=1)}
    p2 <- function(x) {formatC(x, format="f", digits=2)}
    p3 <- function(x) {formatC(x, format="f", digits=3)}
    p4 <- function(x) {formatC(x, format="f", digits=4)}
    p5 <- function(x) {formatC(x, format="f", digits=5)}
    
    logit <-     function(p) log(1/(1/p-1))
    expit <-     function(x) 1/(1/exp(x) + 1)
    inv_logit <- function(logit) exp(logit) / (1 + exp(logit))
    is.even <-   function(x){ x %% 2 == 0 }                       # function to id. odd maybe useful
    options(width=200)



 
```

# Introduction

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r, }

# select the design to simulate
Design = "Treatment interacts with all variables" 
#Design = "Treatment interacts with smoking only" 
#Design = "No-interaction logit-additive model"

# coefficients on log odds scale

intercept <- -3
n=1000
v1 = 1
v2 = 1/(65-18)
v3 = 0.4
v4 = 0
v5 = 1/3
v6 = -.5/10
v7 = 0.25/30
v8 = -.1/10
v9 = -1/50
v10 = log(2)
v11 = -log(1)
v12 = log(0.5)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# for Rshiny needed this separate so could control this
randomi <- runif(n)    # this determine Y=1 later, 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

trt.coef       <-  v1     # log odds ratio so 1 -> 2.718, so 1 is LARGE
age.coef       <-  v2     # log odds of 1 over the age range
smoke.coef     <-  v3     # this is odds of 1.5
bmi.coef       <-  v4     # this is an odds of 1..50:50
covar3.coef    <-  v5     # log odds 1 over range of 3
covar1.coef    <-  v6     # log odds -.05 per unit change
vas.coef       <-  v7     # log odds .008 per unit change. log odds .25 over 30 units odds 1.27
time.coef      <-  v8     # log odds -.01 per year, log odds -.1 over 10 years or odds .90
covar2.coef    <-  v9     # log odds 0.02 per unit, log odds 1 over 50 units or odds 2.7
fact1.coef     <-  v10    # log odds 0.693 per change in binary, or odds of 2   
binary2.coef   <-  v11    # log odds 0 per change in binary, or odds of 1  
sex.coef       <-  v12    # log odds -0.693 per change in binary, or odds of .5  

# made up data structure 
trt      <- sample(1:3,   n, replace=TRUE)      # trt 3 levels
age      <- sample(18:65, n, replace=TRUE)      # continuous
bmi      <- sample(1:3,   n, replace=TRUE)      # assume 3 equal groups
smoking  <- sample(1:3,   n, replace=TRUE)      # categorical assume 3 equal groups
covar3   <- round(runif(n,0,3),2)
covar1   <- round(runif(n,0,10),2)
vas      <- sample(1:30, n, replace=TRUE)
time     <- round(runif(n,0,10),2)              # years
covar2   <- sample(1:50, n, replace=TRUE)
fact1    <- sample(0:1,  n, replace=TRUE)
binary2  <- sample(0:1,  n, replace=TRUE)
sex      <- sample(0:1,  n, replace=TRUE)


```

# Linear predictor

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r, }

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~linear predictor
if ( ( Design) == "Treatment interacts with all variables" )  {
  
  lp = intercept + trt*trt.coef*(smoking*smoke.coef   +   age*age.coef  + bmi*bmi.coef   + covar3*covar3.coef +
                                   covar1*covar1.coef +   vas*vas.coef  + time*time.coef + covar2*covar2.coef +
                                   fact1*fact1.coef   +
                                   binary2*binary2.coef + sex*sex.coef) 
  
}   else if ( ( Design ) == "Treatment interacts with smoking only" ) {    
  
  # truth  only smoking interacts  with trt
  lp = intercept + (trt*trt.coef*smoking*smoke.coef)   +   age*age.coef   + bmi*bmi.coef + covar3*covar3.coef +
    covar1*covar1.coef  + vas*vas.coef   + time*time.coef + covar2*covar2.coef + fact1*fact1.coef +
    binary2*binary2.coef + sex*sex.coef
  
}   else if ( ( Design) == "No-interaction logit-additive model" ) {  
  
  # truth no interactions
  lp = intercept + trt*trt.coef + smoking*smoke.coef + age*age.coef  + bmi*bmi.coef  + covar3*covar3.coef  +
    covar1*covar1.coef + vas*vas.coef  + time*time.coef + covar2*covar2.coef + fact1*fact1.coef +
    binary2*binary2.coef + sex*sex.coef
}

y <- ifelse(randomi < plogis(lp), 1, 0)   # one liner  randomi object is necessary for R shiny only



```

# Dataset creation

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r, }


datx <- data.frame(cbind(y,  trt ,smoking,  age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi))

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
da <-  datx 

da$trt <-     factor(da$trt)
da$smoking <- factor(da$smoking)
da$fact1 <-   factor(da$fact1)
da$binary2 <- factor(da$binary2)
da$sex <-     factor(da$sex)
da$bmi <-     factor(da$bmi)

label(da$age)                <- 'Age'                       # labels for forest plots
label(da$trt)                <- 'Treatment'
label(da$bmi)                <- 'Body Mass Index'
label(da$smoking)            <- 'Smoking'
label(da$covar3)             <- 'Biomarker'
label(da$covar1)             <- 'Blood score'
label(da$vas)                <- 'Visual analogue score'
label(da$time)               <- 'Time since diagnosis'
label(da$covar2)             <- 'Fitness score'
label(da$fact1)              <- "History"
label(da$binary2)            <- "Employed"
label(da$sex)                <- 'Sex'

dd <<- datadist(da)
options(datadist="dd")


```

# Regression

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r, results='asis'}

# RUN REGRESSONS
A<-lrm(y~   trt * (smoking  + age  + bmi + covar3 + covar1 + vas + time + covar2 + fact1 + binary2 +sex),da, y=TRUE ,x=TRUE)  # all interact with trt
B<-lrm(y~  (trt *  smoking) + age  + bmi + covar3 + covar1 + vas + time + covar2 + fact1 + binary2 +sex, da, y=TRUE, x=TRUE)  # smoking * trt only
C<-lrm(y~   trt +  smoking  + age +  bmi + covar3 + covar1 + vas + time + covar2 + fact1 + binary2 +sex, da, y=TRUE, x=TRUE)  # main effect

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# rel explained variation
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# L1 <-   var(predict(B, type='fitted')) / 
#   var(predict(A, type='fitted')) 
# 
# L2 <-   var(predict(C, type='fitted')) / 
#   var(predict(A, type='fitted')) 
# 
# L3 <-   var(predict(C, type='fitted')) / 
#   var(predict(B, type='fitted')) 
# 
# L1
# L2  
# L3 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# LRTESTS
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# k1 <- contrast(A, list(smoking=c(2), trt=c(1:3)), list(smoking=c(1), trt=c(1:3)) , fun=exp) 
# z1 <- print(k1, X=TRUE)   

# lrtest( A, B)

lrtest( A, C)

#lrtest( B, C)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# FULL INTERACTION MODEL SUMMARY
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

(A1 <- summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=1, est.all=FALSE, vnames=c( "labels")))

(A2 <- summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=2, est.all=FALSE, vnames=c( "labels")))

(A3 <- summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=3, est.all=FALSE, vnames=c( "labels")))


# (A1 <- summary(A, smoking=1, age=0, covar3=0, covar1=0, vas=0, time=0, covar2=0, fact1=0, binary2=0, sex=0, bmi=1, trt=1, est.all=FALSE, vnames=c( "labels")))
# 
# (A2 <- summary(A, smoking=1, age=0, covar3=0, covar1=0, vas=0, time=0, covar2=0, fact1=0, binary2=0, sex=0, bmi=1, trt=2, est.all=FALSE, vnames=c( "labels")))
# 
# (A3 <- summary(A, smoking=1, age=0, covar3=0, covar1=0, vas=0, time=0, covar2=0, fact1=0, binary2=0, sex=0, bmi=1, trt=3, est.all=FALSE, vnames=c( "labels")))
# 
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# # SMOKING TRT INTERACTION MODEL SUMMARY
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# 
# (A1 <- summary(B, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=1, est.all=FALSE, vnames=c( "labels")))
# 
# (A2 <- summary(B, smoking=1,   trt=2, est.all=FALSE, vnames=c( "labels")))
# 
# (A3 <- summary(B, smoking=1,   trt=3, est.all=FALSE, vnames=c( "labels")))
# 
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# # MAIN EFFECTS MODEL SUMMARY
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# 
# (A1 <- summary(C, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=1, est.all=FALSE, vnames=c( "labels")))

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Plotting the summaries in forest plots
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

```

# Plot summaries

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r, }

par(mfrow=c(1,3)) 

par(oma=c(3,6,1,1)) 

options(digits=1)

plot(summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=1, est.all=FALSE, vnames=c( "labels")), 
     log=TRUE, xlim=c(log(.01),log(40)),
     q=c(  0.95 ), at=c(.02,0.05,.1,.2,.5,1,2,4,8,20), lwd=3, pch=17,
     col=   rgb(red=.4,green=.1,blue=.5,alpha=c(.5,.3,.2)),
     col.points='black', cex=1, main= "Odds Ratio (Treatment 1)", cex.main=1.8
)

plot(summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=2, est.all=FALSE, vnames=c( "labels")), 
     log=TRUE, xlim=c(log(.01),log(40)),
     q=c(  0.95 ), at=c(.02,0.05,.1,.2,.5,1,2,4,8,20), lwd=3, pch=17,
     col=   rgb(red=.4,green=.1,blue=.5,alpha=c(.5,.3,.2)),
     col.points='black', cex=1, main= "Odds Ratio (Treatment 2)", cex.main=1.8
)

plot(summary(A, smoking=1, age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi=1, trt=3, est.all=FALSE, vnames=c( "labels")), 
     log=TRUE, xlim=c(log(.01),log(40)),
     q=c(  0.95 ), at=c(.02,0.05,.1,.2,.5,1,2,4,8,20), lwd=3, pch=17,
     col=   rgb(red=.4,green=.1,blue=.5,alpha=c(.5,.3,.2)),
     col.points='black', cex=1, main= "Odds Ratio (Treatment 3)", cex.main=1.8
)

par(mfrow=c(1,1))



```

# Presentation of fact1 and treatment interaction

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r, } 

options(digits=6)
k1 <- contrast(A, list(fact1=c(0,1), trt=c(2)), list(fact1=c(0,1), trt=c(1)) , fun=exp) 
z1 <- print(k1, X=TRUE)   

k2 <- contrast(A, list(fact1=c(0,1), trt=c(3)), list(fact1=c(0,1), trt=c(1)) , fun=exp) 
z2 <- print(k2, X=TRUE)   

k3 <- contrast(A, list(fact1=c(0,1), trt=c(3)), list(fact1=c(0,1), trt=c(2)) , fun=exp) 
z3 <- print(k3, X=TRUE)   
#

```

# Presentation of fact1 and treatment interaction plotting

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r, } 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
  ## lets plot
  

int.plot <- function(k1, factor.="factor of interest",
                     effect="Treatment 2 - Treatment 1", 
                     first.grp="Absent", 
                     second.grp="Present") {
  ####inputs
  zz <- k1
  
  # log scale
  Scorex=as.vector(zz$Contrast)
  lbx =  as.vector(zz$Lower)
  ubx =  as.vector(zz$Upper)
  
  require(ggplot2)
  
  df.plot <- data.frame(x=c(effect,effect),
                        factor.=c(first.grp,second.grp ),
                        Score=exp(Scorex),
                        lb = exp(lbx),
                        ub =exp(ubx))
  
  df.plot$factor. = factor(df.plot$factor., 
                           levels = c(first.grp,second.grp ))
  
  
  
  
  df.plot$cord = max(df.plot$ub)
  
  gp <- ggplot(df.plot, aes(x=factor., y=log(Score), fill="black", group=x))
  gg <- gp + #geom_line(aes(linetype=x), size=.6) + 
    geom_point(aes(shape=x), size=3) + 
    geom_errorbar(aes(ymax=log(ub), ymin=log(lb)), width=.1) +
    theme(legend.position="none") + ylab("Odds Ratio (OR > 1 better outcomes) ") + xlab(factor.) +
    
    geom_hline(yintercept=log(1), linetype="dashed", color = "blue") +
    
    scale_y_continuous(
      breaks= log(c(1/32,1/16,1/8, 1/4,1/2,  1, 2, 4 ,8, 16,32,64, 128) )  ,  
      limits = c(log(1/12),log(128)),  
      labels=     c(1/32,1/16,1/8, 1/4,1/2,  1, 2, 4 ,8, 16,32,64,128)
    ) +
    
    coord_flip() +
    
    geom_text(aes(  #y=log(cord*1.5) ,
      y=log(40),
      label = paste0(p3(Score),", 95%CI (" ,p3(lb),", ",p3(ub), ")"), 
      vjust=-1.0), size=2.8, color='blue') +
    
    ggtitle( paste0("Odds ratio of ASAS20 response for ", effect) )
  
  
  gg <- gg + labs(caption = c("Interaction p-value 0.0xx, test the necessity of the orange interaction", 
                              "Interaction present if the pattern differs between factors")) + 
    theme(plot.caption = element_text(hjust=c(1, 0)))
  
  
  i <- gg + geom_segment(
    x = 1.5, y =  Scorex[1],
    xend = 1.5, yend =  Scorex[2],
    lineend = "round", # See available arrow types in example above
    linejoin = "round",
    size = .5, 
    arrow = arrow(length = unit(0.2, "cm")),
    colour = "#EC7014" # Also accepts "red", "blue' etc
  ) 
  
  
  
  k <- i + geom_text( aes(
    x = 1.5, y = (Scorex[1]+Scorex[2])/2,
    label = paste0("Odds of response ",p0(exp(   max(Scorex[2],Scorex[1]) -  min(Scorex[2],Scorex[1])  ))," x"), 
    group = NULL,
    vjust = -1, #.3
    hjust = .7 #1
  ), size=2.8 , color="#EC7014") 
  
  
  #print(k)
}


```

#  contrasts within Factor

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r, } 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
age.=sample(30:80,1)  # showing it is the interaction that counts.
options(digits=6)
k1 <- contrast(A, list(fact1=c(0,1),age=age., trt=c(2)), list(fact1=c(0,1), age=age.,trt=c(1)) , fun=exp) 
z1 <- print(k1, X=TRUE)   

k2 <- contrast(A, list(fact1=c(0,1), age=age.,trt=c(3)), list(fact1=c(0,1), age=age.,trt=c(1)) , fun=exp) 
z2 <- print(k2, X=TRUE)   

k3 <- contrast(A, list(fact1=c(0,1), age=age.,trt=c(3)), list(fact1=c(0,1), age=age.,trt=c(2)) , fun=exp) 
z3 <- print(k3, X=TRUE)   
#

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

#####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
p1x <- int.plot(k1, factor.="factor of interest",
                effect="Treatment 2 - Treatment 1", 
                first.grp="Absent", 
                second.grp="Present") 


p2x <- int.plot(k2, factor.="factor of interest",
                effect="Treatment 3 - Treatment 1", 
                first.grp="Absent", 
                second.grp="Present") 


p3x <-int.plot(k3, factor.="factor of interest",
               effect="Treatment 3 - Treatment 2", 
               first.grp="Absent", 
               second.grp="Present") 

require(gridExtra)

# its only the orange that is important. And will not change if other values in model are altered.
# the actual OR will change if the covariates change, but the same amount in both levels.
# should mention the values that are held constant!
grid.arrange(p1x,p2x,p3x)
# A
# lrtest(A,C)
# anova(A)
 

```

#  contrasts within treatment

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

```{r, } 


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~now
# now try the original approach
age.=sample(30:80,1)  # showing it is the interaction that counts.
options(digits=6)
k1 <- contrast(A, list(fact1=c(1),age=age., trt=c(1)), list(fact1=c(0), age=age.,trt=c(1)) , fun=exp) 
z1 <- print(k1, X=TRUE)   

k2 <- contrast(A, list(fact1=c(1), age=age.,trt=c(2)), list(fact1=c(0), age=age.,trt=c(2)) , fun=exp) 
z2 <- print(k2, X=TRUE)   

k3 <- contrast(A, list(fact1=c(1),  age=age.,trt=c(3)), list(fact1=c(0),  age=age.,trt=c(3)) , fun=exp) 
z3 <- print(k3, X=TRUE)   


zz<-rbind(k1,k2,k3)
zz<-zz[,c("Contrast","Lower","Upper")]
zz<- unlist(zz)
zz<-matrix(zz, nrow=3, ncol=3)
zz<-as.data.frame(zz)
names(zz) <-c("Score","lb","ub")
zz<-data.frame(zz)
zze <- exp(zz)

df.plot <- data.frame(x=c("Treatment","Treatment", "Treatment"),
                      factor.=c("Placebo","150mg","300mg"),
                      Score=exp(zz$Score),
                      lb = exp(zz$lb),
                      ub =exp(zz$ub))


 
 


df.plot$factor. = factor(df.plot$factor., levels = c("Placebo","150mg","300mg"))
df.plot$factor. = factor(df.plot$factor., levels = c("300mg", "150mg", "Placebo"))
 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~START OF GOOD PLOT
 


gp <- ggplot(df.plot, aes(x=factor., y=log(Score), fill="black", group=x))
gg <- gp + #geom_line(aes(linetype=x), size=.6) + 
  geom_point(aes(shape=x), size=3) + 
  geom_errorbar(aes(ymax=log(ub), ymin=log(lb)), width=.1) +
  theme(legend.position="none") + ylab("Odds Ratio") + xlab("Treatment") +
  
  geom_hline(yintercept=log(1), linetype="dashed", color = "blue") +
  
  scale_y_continuous(
    breaks= log(c(1/64,1/32,1/16,1/8, 1/4,1/2,  1, 2, 4 ,8, 16,32,64, 128) )  ,  
    limits = c(log(1/32),log(128)),  
    labels=     c(1/64,1/32,1/16,1/8, 1/4,1/2,  1, 2, 4 ,8, 16,32,64,128)
  ) +
  
  coord_flip() +
 
  
  geom_text(aes(  y=log(40) ,label = paste0(p3(zze$Score),", 95%CI (" ,p3(zze$lb),", ",p3(zze$ub), ")"), 
                  vjust=-1.0), size=2.8, color='blue') +
   
  
  ggtitle( "Nail Dystrophy (Present v Absent) Odds ratio of ASAS20 response by treatment") 

  
gg <- gg + labs(caption = c("Interaction p-value 0.0xx, test the necessity of the two orange interactions", "Interaction present if the pattern differs across treatments\nOdds ratio > 1 better outcomes")) + 
  theme(plot.caption = element_text(hjust=c(1, 0)))
 
i <- gg + geom_segment(
  x = 2.5, y =  zz$Score[1],
  xend = 2.5, yend =  zz$Score[2],
  lineend = "round", # See available arrow types in example above
  linejoin = "round",
  size = .5, 
  arrow = arrow(length = unit(0.2, "cm")),
  colour = "#EC7014" # Also accepts "red", "blue' etc
) 



j <- i + geom_segment(
  x = 1.5, y =  zz$Score[2],
  xend = 1.5, yend =  zz$Score[3],
  lineend = "round", # See available arrow types in example above
  linejoin = "round",
  size = .5, 
  arrow = arrow(length = unit(0.2, "cm")),
  colour = "#EC7014" # Also accepts "red", "blue' etc
) 


k <- j + geom_text( aes(
  x = 2.5, y = (zz$Score[1]+zz$Score[2])/2,
  label = paste0("150mg v placebo odds of response ",
                 p0(exp(   max(zz$Score[2],zz$Score[1]) -  min(zz$Score[2],zz$Score[1])  ))," x "), 
  group = NULL,
  vjust = -1, #.3
  hjust = .5
), size=2.8 , color="#EC7014") 


m <- k + geom_text( aes(
  x = 1.5, y = ((zz$Score[2]+zz$Score[3])/2),
  label = paste0("300mg v placebo odds of response ",
                 p0(exp(   max(zz$Score[3],zz$Score[2]) -  min(zz$Score[3],zz$Score[2])  ))," x "), 
  group = NULL,
  vjust = -1,
  hjust = .5
), size=2.8 , color="#EC7014") 



n <- m + geom_text( aes(
  x = 3, y = log(40),
  label = "OR: Present v Absent", 
  group = NULL,
  vjust = - 3, #.3
  hjust = .5 #1
), size=2.8 , color="blue") 


n
















  

  
```

# xxxxxxxxxxxxxxxxxxxxxx

```{r, }

 
  
     
```

# Computing Environment

`r markupSpecs$html$session()`