---
title: "(i) Show how coordinates of forest plot can be found for interaction model by scaling the regression coeficients and standard error by duplicating R rms summary function and (ii) duplicating anova.rms function"
author: "Eamonn"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  pdf_document:
    toc: true
    toc_depth: 2
  fig_height: 6
  fig_width: 8
header-includes:
- \usepackage{eso-pic,graphicx,transparent}
- \usepackage{graphicx}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \setlength\headheight{22pt}
- \fancyfoot[RO]{Reproducing R functions by hand}
- \usepackage{lastpage}
- \cfoot{Page \thepage\ of \pageref{LastPage}}
---

\newpage  
<!-- \tableofcontents   -->
<!-- \listoffigures -->
<!-- \listoftables -->
\newpage





```{r setup, include=FALSE, echo=FALSE, }
 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#  
# Investigating differential trt effects (logistic regression)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
rm(list=ls())   
set.seed(3333)          # reproducible
knitr::opts_chunk$set(comment = NA)
library(reshape)
library(rms)

options(max.print=1000000)    
options(scipen=999)

## convenience functions
p0 <- function(x) {formatC(x, format="f", digits=1)}
p1 <- function(x) {formatC(x, format="f", digits=1)}
p2 <- function(x) {formatC(x, format="f", digits=2)}
p3 <- function(x) {formatC(x, format="f", digits=3)}
p4 <- function(x) {formatC(x, format="f", digits=4)}
p5 <- function(x) {formatC(x, format="f", digits=5)}

logit <-     function(p) log(1/(1/p-1))
expit <-     function(x) 1/(1/exp(x) + 1)
inv_logit <- function(logit) exp(logit) / (1 + exp(logit))
is.even <-   function(x){ x %% 2 == 0 }                       # function to id. odd maybe useful
options(width=200)

# select the design to simulate
#Design = "Treatment interacts with all variables" 
Design = "Treatment interacts with smoking only" 
#Design = "No-interaction logit-additive model"

# coefficients on log odds scale

intercept <- -3
n=1000
v1 = 1
v2 = 1/(65-18)
v3 = 0.4
v4 = 0
v5 = 1/3
v6 = -.5/10
v7 = 0.25/30
v8 = -.1/10
v9 = -1/50
v10 = log(2)
v11 = -log(1)
v12 = log(0.5)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# for Rshiny needed this separate so could control this
randomi <- runif(n)    # this determine Y=1 later, 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

trt.coef       <-  v1     # log odds ratio so 1 -> 2.718, so 1 is LARGE
age.coef       <-  v2     # log odds of 1 over the age range
smoke.coef     <-  v3     # this is odds of 1.5
bmi.coef       <-  v4     # this is an odds of 1..50:50
covar3.coef    <-  v5     # log odds 1 over range of 3
covar1.coef    <-  v6     # log odds -.05 per unit change
vas.coef       <-  v7     # log odds .008 per unit change. log odds .25 over 30 units odds 1.27
time.coef      <-  v8     # log odds -.01 per year, log odds -.1 over 10 years or odds .90
covar2.coef    <-  v9     # log odds 0.02 per unit, log odds 1 over 50 units or odds 2.7
fact1.coef     <-  v10    # log odds 0.693 per change in binary, or odds of 2   
binary2.coef   <-  v11    # log odds 0 per change in binary, or odds of 1  
sex.coef       <-  v12    # log odds -0.693 per change in binary, or odds of .5  

# made up data structure 
trt      <- sample(1:3,   n, replace=TRUE)      # trt 3 levels
age      <- sample(18:65, n, replace=TRUE)      # continuous
bmi      <- sample(1:3,   n, replace=TRUE)      # assume 3 equal groups
smoking  <- sample(1:3,   n, replace=TRUE)      # categorical assume 3 equal groups
covar3   <- round(runif(n,0,3),2)
covar1   <- round(runif(n,0,10),2)
vas      <- sample(1:30, n, replace=TRUE)
time     <- round(runif(n,0,10),2)              # years
covar2   <- sample(1:50, n, replace=TRUE)
fact1    <- sample(0:1,  n, replace=TRUE)
binary2  <- sample(0:1,  n, replace=TRUE)
sex      <- sample(0:1,  n, replace=TRUE)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~linear predictor
if ( ( Design) == "Treatment interacts with all variables" )  {
  
  lp = intercept + trt*trt.coef*(smoking*smoke.coef   +   age*age.coef  + bmi*bmi.coef   + covar3*covar3.coef +
                                   covar1*covar1.coef +   vas*vas.coef  + time*time.coef + covar2*covar2.coef +
                                   fact1*fact1.coef   +
                                   binary2*binary2.coef + sex*sex.coef) 
  
}   else if ( ( Design ) == "Treatment interacts with smoking only" ) {    
  
  # truth  only smoking interacts  with trt
  lp = intercept + (trt*trt.coef*smoking*smoke.coef)   +   age*age.coef   + bmi*bmi.coef + covar3*covar3.coef +
    covar1*covar1.coef  + vas*vas.coef   + time*time.coef + covar2*covar2.coef + fact1*fact1.coef +
    binary2*binary2.coef + sex*sex.coef
  
}   else if ( ( Design) == "No-interaction logit-additive model" ) {  
  
  # truth no interactions
  lp = intercept + trt*trt.coef + smoking*smoke.coef + age*age.coef  + bmi*bmi.coef  + covar3*covar3.coef  +
    covar1*covar1.coef + vas*vas.coef  + time*time.coef + covar2*covar2.coef + fact1*fact1.coef +
    binary2*binary2.coef + sex*sex.coef
}

y <- ifelse(randomi < plogis(lp), 1, 0)   # one liner  randomi object is necessary for R shiny only

datx <- data.frame(cbind(y,  trt ,smoking,  age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi))

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
da <-  datx 

da$trt <-     factor(da$trt)
da$smoking <- factor(da$smoking)
da$fact1 <-   factor(da$fact1)
da$binary2 <- factor(da$binary2)
da$sex <-     factor(da$sex)
da$bmi <-     factor(da$bmi)

label(da$age)                <- 'Age'                       # labels for forest plots
label(da$trt)                <- 'Treatment'
label(da$bmi)                <- 'Body Mass Index'
label(da$smoking)            <- 'Smoking'
label(da$covar3)             <- 'Biomarker'
label(da$covar1)             <- 'Blood score'
label(da$vas)                <- 'Visual analogue score'
label(da$time)               <- 'Time since diagnosis'
label(da$covar2)             <- 'Fitness score'
label(da$fact1)              <- "History"
label(da$binary2)            <- "Employed"
label(da$sex)                <- 'Sex'

dd <<- datadist(da)
options(datadist="dd")

```
# Summary function (useful to obtain coordinates for forest plot)
## Reproduce summary rms function on logistic regression with treatment 1 as reference level on simulated data

```{r effect0, include=TRUE, echo=TRUE}
  
  # I have simulated data (da) that I use to show how to reproduce R functions 
  # Make treatment 1  reference level, 
  da$trt <- relevel(da$trt, ref= "1")
  
  # model in which we analyse all vars interacting with treatment
  (A <- lrm(y~   trt * (smoking  + age  + bmi + covar3 + covar1 + 
                       vas + time + covar2 + fact1 + binary2 +sex),da, y=TRUE ,x=TRUE) ) 


```
\newpage
## Reproduce summary rms function on logistic regression with treatment 1 as reference level on age only using simulated data

```{r effect1, include=TRUE, echo=TRUE}

  variable <- "age"
  
  # estimate effect over the following age range
  # note there are at least 9 diff ways to calculate percentiles R and SAS use different defaults, 
  # this can make a difference! type option controls this in R
  Ty=2 # select percentile method
  (low<-quantile(da$age, probs = c(.25), type=Ty))  # low age
  (upp<-quantile(da$age, probs = c(.75), type=Ty))  # high age
  
  # this is Frank Harrell's built in summary function we want to reproduce age effect by 'hand'
  (A1 <- summary(A, age=c(low,upp),  trt=1, est.all=FALSE, vnames=c( "labels"))) 
  
  # get the variance covariance matrix, standard error (se) is here or
  # get it from regression table
  var <- vcov(A)   
  
  # range
  diff <- upp-low 
  
  # rescale the effect of variable (reg coefficient) on log odds of response, 
  # the coefficient is over 1 unit by default in regression table
  (eff <- coef(A)[variable][[1]]*diff) 
  
  # rescale standard error from model or sqrt covariance from matrix
  se <-  diff*sqrt(diag(var)[variable][[1]]) 
  
  # here are our estimates, we successfully reproduce the summary function, 
  # these can be coordinates in forest plot for treatment 1
   res <- c(eff,  se, (eff+c(-1,1)* qnorm(.975)*se))
   names(res )  <- c( 'Effect','S.E.','Lower 0.9','Upper 0.95')
   res
```
\newpage
## Reproduce summary rms function on logistic regression with treatment 2 as reference level on age only using simulated data

```{r effect2, include=TRUE, echo=TRUE}

  # Now make treatment 2 the reference level and repeat
  da$trt <- relevel(da$trt, ref= "2")
  
  # all vars interact with trt
  (A <- lrm(y~   trt * (smoking  + age  + bmi + covar3 + covar1 + 
                       vas + time + covar2 + fact1 + binary2 +sex),da, y=TRUE ,x=TRUE) ) 
  
  # this is Frank Harrell's built in summary function, we want to reproduce age effect by 'hand'
  (A1 <- summary(A, age=c(low,upp),  trt=2, est.all=FALSE, vnames=c( "labels"))) 
  
  # get the variance covariance matrix, standard error (se) is here or
  # get it from regression table
  var <- vcov(A)   
  
  diff <- upp-low  # range
  
  # rescale the effect of variable on log odds of response using diff,
  # the coefficient is effect on reponse over 1 unit by default in regression table
  (eff <- coef(A)[variable][[1]]*diff)   
 
  # rescale standard error from model sqrt of covariance matrix or get se from reg table
  se <-  diff*sqrt(diag(var)[variable][[1]])  
  
  # here are our estimates, we successfully reproduce the summary function
  # these can be coordinates in forest plot for treatment 1
   res <- c(eff,  se, (eff+c(-1,1)* qnorm(.975)*se))
   names(res )  <- c( 'Effect','S.E.','Lower 0.9','Upper 0.95')
   res
 
  
  
``` 

\newpage
# ANOVA function (use this info to construct anova table and dot plot)
## Reproduce anova rms function, first show simple example for interaction effect of age only

```{r anova0, include=TRUE, echo=TRUE}

     # text that we will use to select information
     ref="* age"

    # run smaller regression
    A <- lrm(y~ trt * (age ),da, y=TRUE ,x=TRUE)  

    # This is the ANOVA function that want to reproduce
    x <- anova(A, india=FALSE, vnames='labels' )
    print(x, which=c( 'subscripts' ))
 
    # get the variance covariance matrix without intercept
    cov <- vcov(A, regcoef.only = TRUE, intercepts = "none") 
    
    # select only information of interest
    c1 <- cov[grepl(ref, rownames(cov)), grepl(ref, colnames(cov))  ]
    
    # labels of interest
    idx <- colnames(c1) 
    # select regression coefficients of interest
    co <-  A$coefficients[idx] 
    # show selected information of interest from variance covariance matrix
    cov[idx, idx] 
    # solvet function solves the equation a %*% x = b for x, #
    # where b can be either a vector or a matrix. a is square
    
    chi <- co %*% solvet( cov[idx, idx], co )
    
    # so regression coeff %*% solvet gives chi square
    # so covariance %*% solvet solution will give the regression coefficients
    
    df. = length(idx)
    pvalue =(1 - pchisq(chi, df.))
   
    # here are our estimates, we successfully reproduce the anova function above
    res <- cbind(chi, df. , pvalue)
    res <- as.data.frame(res)
    names(res) <- c("Chi-square","d.f.","P")
    print(res)
    
    

  
``` 

\newpage
## Reproduce anova rms function on more variables 

```{r anova1, include=TRUE, echo=TRUE  }

    # run regression
    A <- lrm(y~ trt * (smoking  + age  + bmi + covar3 + covar1 + vas + 
                         time + covar2 + fact1 + binary2 +sex),da, y=TRUE ,x=TRUE)  

    # This is the ANOVA function that want to reproduce
    x <- anova(A, india=FALSE, vnames='labels' )
    print(x, which=c( 'subscripts' ))
 
    # get the variance covariance matrix without intercept
    cov <- vcov(A, regcoef.only = TRUE, intercepts = "none") 
    
    cov[1:3,1:3] # show first 3 columns and rows
    
    # working on the text here...
    namez2 <- colnames(cov)                     # capture factor names
    namez <- gsub(".*\\*","", colnames(cov))    # remove text starting and including *
    namez <-  gsub("(.*)\\=.*", "\\1", namez )  # remove text starting and including =
    namez <- unique(namez)                      
    
    at <- A$Design
    labels <- at$label
    
   # empty matrix in which to collect information 
   res <- matrix(, nrow = length(labels), ncol = 4)
    
     # loop to create anova table
     for ( i in 1 : length(namez))  {
       # select parameter we are interested in
       par <- namez[i]                   
       # select appropriate data from var covar matrix
       c1 <- cov[grepl(par, rownames(cov)), grepl(par, colnames(cov))  ]   
       # get the names of columns
       idx <- colnames(c1)   
       # select regression coefficients of interest
       co <-  A$coefficients[idx]
     
     # do the calculations. solvet is function solves the equation a %*% x = b for x, 
     # where b can be either a vector or a matrix. a is square
     chi <- co %*% solvet( c1, co )  # chi square value
     df. <- length(idx)              # degrees of freedom
     pvalue <-(1 - pchisq(chi, df.)) # p-value
        
    res[i,]  <- c(labels[i], chi, df., pvalue)  # collect information
       
     }
    
    # here are our estimates, we successfully reproduce the rms anova function above
    res <- as.data.frame(res)
    names(res) <- c("Factor","Chi-square","d.f.","P")
    print(res)

``` 

\newpage
## Reproduce anova rms function TOTAL row

```{r anova2, include=TRUE, echo=TRUE }

    # total, use the whole variance covariance matrix
    idx <- colnames(cov)
    co <-  A$coefficients[-1] 
    
    # function solves the equation a %*% x = b for x as before
    chi <- co %*% solvet( cov, co )
    df. = length(idx)
    pvalue =(1 - pchisq(chi, df.))

    res <- cbind(chi, df. , pvalue)
    res <- as.data.frame(res)
    names(res) <- c("Chi-square","d.f.","P")
    # here are our estimates, we successfully reproduce the rms anova function above
    print(res)
    

``` 

\newpage
## Reproduce anova rms on TOTAL INTERACTION row

```{r anova3, include=TRUE, echo=TRUE}    
    
    # all interactions only, use the whole variance covariance matrix
    # variance covariance matrix without intercept
    cov <- vcov(A, regcoef.only = TRUE, intercepts = "none") 
    # extract names if they contain *
    idx <- colnames(cov)[grepl("*", colnames(cov), fixed=TRUE)]  
    # extract var covariance info  of interest
    c1 <-  cov[(idx),(idx)]    
    # extract reg coefficients only with * in name
    co <- A$coefficients[idx] 
    
    idx # information of interest
    c1  # covariance matrix information of interest
    co  # regression coefficients of interest
    
    # function solves the equation a %*% x = b for x, 
    # where b can be either a vector or a matrix. a is square
    chi <- co %*% solvet( c1, co )
    df. = length(idx)
    pvalue =(1 - pchisq(chi, df.))
    
    
    res <- cbind(chi, df. , pvalue)
    res <- as.data.frame(res)
    names(res) <- c("Chi-square","d.f.","P")
    # here are our estimates, we successfully reproduce the rms anova function above
    print(res)
    
    
 