---
title: "showing how coordinates of forest plot can be found for interaction model, scaling the regression coef and se and duplicating rms summary"
author: "Eamonn"
date: '`r format(Sys.time(), "%d %B, %Y")`'
header-includes:
- \usepackage{eso-pic,graphicx,transparent}
- \usepackage{graphicx}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \setlength\headheight{22pt}
- \fancyhead[L]{\includegraphics[width=2.5cm]{}}
- \fancyfoot[RO]{test}
- \usepackage{lastpage}
- \cfoot{Page \thepage\ of \pageref{LastPage}}
output: html_document

---


\AddToShipoutPictureFG{
  \AtPageCenter{% or \AtTextCenter
    \makebox[0pt]{\rotatebox[origin=c]{45}{%
      \scalebox{5}{\texttransparent{0.3}{ }}%
    }}
  }
}

```{r setup, include=FALSE, echo=FALSE, }
 

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#  
# Investigating differential trt effects (logistic regression)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
rm(list=ls())   
set.seed(3333)          # reproducible

library(reshape)
library(rms)

options(max.print=1000000)    
options(scipen=999)

## convenience functions
p0 <- function(x) {formatC(x, format="f", digits=1)}
p1 <- function(x) {formatC(x, format="f", digits=1)}
p2 <- function(x) {formatC(x, format="f", digits=2)}
p3 <- function(x) {formatC(x, format="f", digits=3)}
p4 <- function(x) {formatC(x, format="f", digits=4)}
p5 <- function(x) {formatC(x, format="f", digits=5)}

logit <-     function(p) log(1/(1/p-1))
expit <-     function(x) 1/(1/exp(x) + 1)
inv_logit <- function(logit) exp(logit) / (1 + exp(logit))
is.even <-   function(x){ x %% 2 == 0 }                       # function to id. odd maybe useful
options(width=200)

# select the design to simulate
#Design = "Treatment interacts with all variables" 
Design = "Treatment interacts with smoking only" 
#Design = "No-interaction logit-additive model"

# coefficients on log odds scale

intercept <- -3
n=1000
v1 = 1
v2 = 1/(65-18)
v3 = 0.4
v4 = 0
v5 = 1/3
v6 = -.5/10
v7 = 0.25/30
v8 = -.1/10
v9 = -1/50
v10 = log(2)
v11 = -log(1)
v12 = log(0.5)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# for Rshiny needed this separate so could control this
randomi <- runif(n)    # this determine Y=1 later, 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

trt.coef       <-  v1     # log odds ratio so 1 -> 2.718, so 1 is LARGE
age.coef       <-  v2     # log odds of 1 over the age range
smoke.coef     <-  v3     # this is odds of 1.5
bmi.coef       <-  v4     # this is an odds of 1..50:50
covar3.coef    <-  v5     # log odds 1 over range of 3
covar1.coef    <-  v6     # log odds -.05 per unit change
vas.coef       <-  v7     # log odds .008 per unit change. log odds .25 over 30 units odds 1.27
time.coef      <-  v8     # log odds -.01 per year, log odds -.1 over 10 years or odds .90
covar2.coef    <-  v9     # log odds 0.02 per unit, log odds 1 over 50 units or odds 2.7
fact1.coef     <-  v10    # log odds 0.693 per change in binary, or odds of 2   
binary2.coef   <-  v11    # log odds 0 per change in binary, or odds of 1  
sex.coef       <-  v12    # log odds -0.693 per change in binary, or odds of .5  

# made up data structure 
trt      <- sample(1:3,   n, replace=TRUE)      # trt 3 levels
age      <- sample(18:65, n, replace=TRUE)      # continuous
bmi      <- sample(1:3,   n, replace=TRUE)      # assume 3 equal groups
smoking  <- sample(1:3,   n, replace=TRUE)      # categorical assume 3 equal groups
covar3   <- round(runif(n,0,3),2)
covar1   <- round(runif(n,0,10),2)
vas      <- sample(1:30, n, replace=TRUE)
time     <- round(runif(n,0,10),2)              # years
covar2   <- sample(1:50, n, replace=TRUE)
fact1    <- sample(0:1,  n, replace=TRUE)
binary2  <- sample(0:1,  n, replace=TRUE)
sex      <- sample(0:1,  n, replace=TRUE)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~linear predictor
if ( ( Design) == "Treatment interacts with all variables" )  {
  
  lp = intercept + trt*trt.coef*(smoking*smoke.coef   +   age*age.coef  + bmi*bmi.coef   + covar3*covar3.coef +
                                   covar1*covar1.coef +   vas*vas.coef  + time*time.coef + covar2*covar2.coef +
                                   fact1*fact1.coef   +
                                   binary2*binary2.coef + sex*sex.coef) 
  
}   else if ( ( Design ) == "Treatment interacts with smoking only" ) {    
  
  # truth  only smoking interacts  with trt
  lp = intercept + (trt*trt.coef*smoking*smoke.coef)   +   age*age.coef   + bmi*bmi.coef + covar3*covar3.coef +
    covar1*covar1.coef  + vas*vas.coef   + time*time.coef + covar2*covar2.coef + fact1*fact1.coef +
    binary2*binary2.coef + sex*sex.coef
  
}   else if ( ( Design) == "No-interaction logit-additive model" ) {  
  
  # truth no interactions
  lp = intercept + trt*trt.coef + smoking*smoke.coef + age*age.coef  + bmi*bmi.coef  + covar3*covar3.coef  +
    covar1*covar1.coef + vas*vas.coef  + time*time.coef + covar2*covar2.coef + fact1*fact1.coef +
    binary2*binary2.coef + sex*sex.coef
}

y <- ifelse(randomi < plogis(lp), 1, 0)   # one liner  randomi object is necessary for R shiny only

datx <- data.frame(cbind(y,  trt ,smoking,  age, covar3, covar1, vas, time, covar2, fact1, binary2, sex, bmi))

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
da <-  datx 

da$trt <-     factor(da$trt)
da$smoking <- factor(da$smoking)
da$fact1 <-   factor(da$fact1)
da$binary2 <- factor(da$binary2)
da$sex <-     factor(da$sex)
da$bmi <-     factor(da$bmi)

label(da$age)                <- 'Age'                       # labels for forest plots
label(da$trt)                <- 'Treatment'
label(da$bmi)                <- 'Body Mass Index'
label(da$smoking)            <- 'Smoking'
label(da$covar3)             <- 'Biomarker'
label(da$covar1)             <- 'Blood score'
label(da$vas)                <- 'Visual analogue score'
label(da$time)               <- 'Time since diagnosis'
label(da$covar2)             <- 'Fitness score'
label(da$fact1)              <- "History"
label(da$binary2)            <- "Employed"
label(da$sex)                <- 'Sex'

dd <<- datadist(da)
options(datadist="dd")

```

### trt 1 is reference

```{r effect0, include=TRUE, echo=TRUE}

da$trt <- relevel(da$trt, ref= "1")

A<-lrm(y~   trt * (smoking  + age  + bmi + covar3 + covar1 + vas + time + covar2 + fact1 + binary2 +sex),da, y=TRUE ,x=TRUE)  # all interact with trt

A

```

### focus on age

```{r effect1, include=TRUE, echo=TRUE}


variable <- "age"

# estimate effect over this range
low<-30  # low age
upp<-60  # high age


low<-1  # low age
upp<-1.5  # high age

# built in function we want to reproduce by 'hand'
(A1 <- summary(A, age=c(low,upp),  trt=1, est.all=FALSE, vnames=c( "labels"))) 

var <- vcov(A)   # variance covariance matrix , se is here or get it from regression table

(diff <- upp-low)

(eff <- coef(A)[variable][[1]]*diff)


se <-  diff*sqrt(diag(var)[variable][[1]])  # or standard error from model  sqrt covariance , or Se from reg table

# here is our estimates
c(eff,
  se,
  (eff+c(-1,1)*     qnorm(.975)*se))
 
```

### trt 2 is reference now

```{r effect2, include=TRUE, echo=TRUE}

da$trt <- relevel(da$trt,ref= "2")

A<-lrm(y~   trt * (smoking  + age  + bmi + covar3 + covar1 + vas + time + covar2 + fact1 + binary2 +sex),da, y=TRUE ,x=TRUE)  # all interact with trt
A

(A1 <- summary(A, age=c(low,upp),  trt=2, est.all=FALSE, vnames=c( "labels")))

#relevel model trt dp treat 1 is refernce level
 


eff <- coef(A)[variable][[1]]*diff

var <- vcov(A)   # variance covariance matrix , se is here or get it from regression table


se <-  diff*sqrt(diag(var)[variable][[1]])  # or standard error from model   # sqrt covariance , or Se from reg table

c(eff,
  se,
  (eff+c(-1,1)*     qnorm(.975)*se))

``` 

### anova

```{r anova, include=TRUE, echo=TRUE}

    x <- anova(A, india=FALSE, vnames='labels' )
    print(x, which=c( 'subscripts' ))

    A <- lrm(y~   trt * ( age  ),da, y=TRUE ,x=TRUE)  # all interact with trt

    x <- anova(A, india=FALSE, vnames='labels' )
    print(x, which=c( 'subscripts' ))
   
    cov <- vcov(A, regcoef.only = TRUE, intercepts = "none") 
    cov
  
    ref="trt" 
    ref="age"
    ref="* age"

    c1 <- cov[grepl(ref, rownames(cov)), grepl(ref, colnames(cov))  ]
    
    idx <- colnames(c1)
    co <-  A$coefficients[idx]
    
    # function solves the equation a %*% x = b for x, where b can be either a vector or a matrix. a is square
    (chi <- co %*% solvet( cov[idx, idx], co ))
    (df. = length(idx))
    (pvalue =(1 - pchisq(chi, df.)))
   
    
    ## total, use the whole variance covariance matrix
    idx <- colnames(cov)
    co <-  A$coefficients[-1] 
    
    # function solves the equation a %*% x = b for x, where b can be either a vector or a matrix. a is square
    (chi <- co %*% solvet( cov, co ))
    (df. = length(idx))
    (pvalue =(1 - pchisq(chi, df.)))
   
    
``` 

### anova

```{r anova, include=TRUE, echo=TRUE}
  
    
    cov <- vcov(A, regcoef.only = TRUE, intercepts = "none") 
  
    ref="trt" 
    ref="age"
    ref="* age"

    c1 <- cov[grepl(ref, rownames(cov)), grepl(ref, colnames(cov))  ]
    
    idx <- colnames(c1)
    co <-  A$coefficients[idx]
    
    # function solves the equation a %*% x = b for x, where b can be either a vector or a matrix. a is square
    (chi <- co %*% solvet( cov[idx, idx], co ))
    (df. = length(idx))
    (pvalue =(1 - pchisq(chi, df.)))
   
    
    ## total, use the whole variance covariance matrix
    idx <- colnames(cov)
    co <-  A$coefficients[-1] 
    
    # function solves the equation a %*% x = b for x, where b can be either a vector or a matrix. a is square
    (chi <- co %*% solvet( cov, co ))
    (df. = length(idx))
    (pvalue =(1 - pchisq(chi, df.)))
    
    
   

```


```{r}

    namez <- gsub(".*\\*","", names(coef(A)))[-1]
      
   
    cov <- vcov(A, regcoef.only = TRUE, intercepts = "none") 

     for ( i in 1 : length(namez))  {
       
       par <- namez[i]
       c1 <- cov[grepl(par, rownames(cov)), grepl(par, colnames(cov))  ]
       idx <- colnames(c1)
       co <-  A$coefficients[idx]
       
       
       
       
     }
    



 